\bf Range Analysis for the IonMonkey JavaScript engine

### 2012-05-02 project-writings/paper.tex
expound a bit upon beta nobes
rename Cytron citation since vim's make parsing was getting confused when there was an error

The approach we took, again following \cite{Gough94eliminatingrange},
is to instead attack the problem in ``SSA style'', by introducing
$\beta$-nodes, a new form of pseudo-operation that associates range
information with a value. $\beta$ nodes take one argument and
additionally have an auxiliary constant range associated with
them. Operationally, $\beta$-nodes are simply copies, but the
invariant is maintained that the output value will fall inside the
range given by the $\beta$ node. Gough and Klaeren refer to SSA
extended with $\beta$ nodes as XSA.

@@

\subsection{Inserting and Removing Beta Nodes}
To put programs in XSA form, Gough and Klaeren presented an extension
to Cytron et al.'s standard algorithm for computing SSA form using
dominance frontiers \cite{Cytron:1991:ECS:115372.115320}.

>>>>

The approach we took, again following \cite{Gough94eliminatingrange},
is to instead attack the problem in ``SSA style'', by introducing
$\beta$-nodes, a new form of pseudo-operation that associates range
information with a value. $\beta$ nodes take one argument and
additionally have an auxiliary constant range associated with
them. Operationally, $\beta$-nodes are simply copies, but the
invariant is maintained that the output value will fall inside the
range given by the $\beta$ node. Gough and Klaeren refer to SSA
extended with $\beta$ nodes as XSA. These $\beta$ nodes are used to split
definitions at conditionally taken branches, and augment uses inside the
branches with range information.

@@

\subsection{Inserting and Removing Beta Nodes}
To put programs in XSA form, Gough and Klaeren presented an extension
to Cytron et al.'s standard algorithm for computing SSA form using
dominance frontiers \cite{Cytron}.
